Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-29 ms.tex
showing time-dependence of illumination gradient.

>>>>

We also examine the slope and intercept of the illumination as a function of time.
It is clear that there is a gradient in the image that also correlates with the flux.
This may explain detector 490's different behavior over time.

\begin{figure*}
\gridline{
\fig{illum_slope_and_intercept.pdf}{0.49\textwidth}{Illumination Gradient Change over Time}
}
\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detector 487..}\label{fig:illumGradientChangeOverTime}
\end{figure*}
